Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-14 analysis/paper/paper.Rmd
Update y-axis code for figure 1
Cleaner code

ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  ylab("Tiller Sheath Blight Incidence (%)") +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```

>>>>

ggplot(RAW_data,
       aes(x = DAI,
           y = TShB_incidence,
           linetype = NRTE,
           shape = NRTE)) +
  stat_summary(fun.y = "mean",
               geom = "line",
               aes(group = TRT)) +
  stat_summary(fun.y = "mean",
               geom = "point",
               aes(group = TRT)) +
  scale_y_continuous(labels = function(x) paste0(x*100),
                     limits = c(0, 1),
                     name = "Tiller Sheath Blight Incidence (%)") +
  scale_shape_discrete(labels = c(expression(N[0]),
                                  expression(N[1]),
                                  expression(N[2]),
                                  expression(N[3]),
                                  expression(N[4]))) +
  scale_linetype_discrete(labels = c(expression(N[0]),
                                     expression(N[1]),
                                     expression(N[2]),
                                     expression(N[3]),
                                     expression(N[4]))) +
  xlab("Days After Inoculation") +
  facet_grid(WMGT ~ YEAR,
             scales = "free_x") +
  labs(linetype = "N Treatment",
       shape = "N Treatment") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  theme(legend.position = "bottom") +
  guides(linetype = guide_legend(nrow = 2),
         shape = guide_legend(nrow = 2))
```
